### 2019-10-10 manuscript/manuscript.rmd
kernel re-ran, mscript knittrd
angle x axis labels

---
csl: plos.csl
output:
  html_document: default
  pdf_document: default
  github_document: default
bibliography: manuscript.bib
---

@@

analyses_new %>% 
	ggplot( aes(x=model_summary, y=clade, col=result, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```

>>>>

---
csl: plos.csl
output:
  pdf_document: default
  github_document: default
  html_document: default
bibliography: manuscript.bib
---

@@

analyses_new %>% 
	ggplot( aes(x=model_summary, y=clade, col=result, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1))
```
